A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-09-06 paper/ms.tex
update ms

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.5\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show that
  Kepler\,1627 is a member of the \clusterage\ old $\delta$~Lyr
  cluster using kinematic information from Gaia, stellar rotation
  periods from TESS, and Li abundances from ground-based spectra.  To
  our knowledge, Kepler\,1627Ab is the youngest planet with a precise
  age yet found by the main Kepler mission.  From unresolved
  starspot-crossing events in the Kepler photometry and
  a Keck/HIRES transit we find that the planet is likely on an
  orbit aligned with the stellar spin axis.  We also briefly explore the flare
  arrival time distribution in the short-cadence Kepler
  photometry.
  The $\delta$~Lyr cluster is one of many stellar groups whose
  properties have been clarified using the Gaia data; many other new
  clusters also overlap with confirmed and candidate exoplanets.
  Verifying the results of Gaia clustering analyses using TESS rotation
  periods seems likely to be an effective path toward expanding the census of
  age-dated planets, and our understanding of planetary evolution.
\end{abstract}

@@

%TODO: might want to revise this text to better frame the boil-off phase...
%TODO: better citations on radius evolution?
For instance, the ``mini-Neptunes'', thought to be made of molten
rocky cores \citep{kite_atmosphere_2020} and extended atmospheric
envelopes of hydrogen and helium, are expected to shrink in size by
factors of several over their first $10^8$ years
\citep{owen_atmospheres_2016,owen_constraining_2020}.  Specifically,
they start with sizes of 4--12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2--4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years of the disk's pressure
support being removed \citep{owen_atmospheres_2016}, the combination of stellar
irradiation and internal heat may also power a more
gradual outflow which can eventually deplete or entirely strip the
envelope from the rocky core
\citep{Owen_Wu_2013,ginzburg_corepowered_2018}.  Discovering young
planets, measuring their masses, and detecting their atmospheric
outflows are key steps toward testing this paradigm, which is often
invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017}.

The K2 and TESS missions have now enabled the detection of about ten
close-in planets younger than 100 million years, all smaller than
Jupiter
\citep{Mann_K2_33b_2016,David_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,plavchan_planet_2020,rizzuto_tess_2020}.
The Kepler mission however has not yielded any planets with precise
ages below one gigayear \citep{Meibom_et_al_2013}.  The reason is that
at the time of the main Kepler mission (2009--2013), only four open
clusters were known in the Kepler field: NGC\,6866, NGC\,6811,
NGC\,6819, and NGC\,6791, with ages spanning 0.7\,Gyr to 9\,Gyr
\citep{meibom_kepler_2011}.  Since that time, analyses of the
kinematic, photometric, and astrometric Gaia data have expanded our
knowledge of open cluster and moving group memberships \citep[{\it
e.g.},][]{cantatgaudin_gaia_2018,zari_3d_2018,kounkel_untangling_2019,Meingast2021,kerr_stars_2021}.
As part of our Cluster Difference Imaging Photometric Survey (CDIPS,
\citealt{bouma_cdipsI_2019}), we concatenated the available analyses
from the literature, which yielded a list of candidate young and
age-dated stars (see Appendix~\ref{app:targetlist}).

@@

A previous clustering analysis of the Gaia data reported that
Kepler\,1627 (KIC 6184894; KOI 5245; TIC 120105470) is a member of the
\cn\ \citep{kounkel_untangling_2019}.  Given the previous statistical
validation the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we examined the age of the star and its putative host cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and that \sn\ is indeed a member
of the cluster.  Focusing on the planet itself,
we confirm that despite the presence of a previously unreported binary companion,
the planet orbits the G-dwarf primary star on an orbit that appears aligned
with the stellar rotation axis
(Section~\ref{sec:planet}).  We conclude by
highlighting broader implications for our ability to age-date a
statistical sample of planets (Section~\ref{sec:conc}).

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored
    points are kinematically selected members of the $\delta$\,Lyr
    cluster.  Both Kepler (gray squares) and TESS observed portions of
    the cluster.  Naked-eye stars ($m_{\rm V}<6.5$) are shown in gray;
    four of them (orange circles) have their names annotated.
    Kepler\,1627 (green star) was observed during the entirety of the
    Kepler mission, and has been observed by TESS for two lunar months
    to date.  The colors of the other cluster members indicate the
    number of TESS sectors during which they have been observed.
    \label{fig:skychart}
	}
\end{figure}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f15c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is \clusterage\ old.}  {\it Top:}
    Color-magnitude diagram of the \cn, IC\,2602 ($\approx35$\,Myr),
    the Pleiades ($\approx 115$\,Myr; \citealt{dahm_2015}), and the
    field (gray).  The right panel provides a zoomed
    view of stars on the pre-main-sequence.  The \cn\ and IC\,2602 are
    approximately the same isochronal age.  {\it Bottom:} TESS and
    Kepler stellar rotation periods versus dereddened Gaia colors, with
    the Pleiades and Praesepe (650\,Myr) shown for
    reference \citep{rebull_rotation_2016a,douglas_poking_2017}.
    The \cn\ is gyrochronally younger than the Pleiades.
   \label{fig:age}
	}
\end{figure*}

@@

We meaured the isochrone age using an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-magnitude diagram (CMD)
of stars in the \cn, IC\,2602, the Pleiades, and the field.  The stars
shown in the \cn\ are selected based on their positions and
kinematics, as discussed in Appendix~\ref{app:kinematicselection}.
Those from the Pleiades and IC\,2602 are adopted from
\citet{cantatgaudin_gaia_2018}, and the field stars are from the Gaia
EDR3 Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following identical data filtering criteria discussed in Appendix~B of
\citet{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}},
and by then applying the extinction coefficients $k_X\equiv A_X/A_0$
computed by \citet{GaiaCollaboration2018} while assuming that $A_0 =
3.1 E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this procedure
yielded a respective mean and standard deviation for the reddening of
$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.  These
values agree reasonably well with previously reported values from the
literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,kounkel_untangling_2019,bossini_age_2019}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and are
therefore approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between these
latter two groups.  To turn this heuristic interpolation into an
age measurement, we used the empirical procedure
developed by \citet{gagne_mutau_2020}.  In brief, we fitted the
pre-main-sequence loci of a set of reference clusters, and the locus
of the target \cn\ was then modeled as a piecewise linear combination
of these reference clusters.  For our reference clusters, we adopted
members of UCL, IC\,2602, and the Pleiades from
\citet{damiani_stellar_2019} and \cite{CantatGaudin2018a}
respectively.  We removed binaries by requiring $\texttt{RUWE}<1.3$,
$\texttt{radial\_velocity\_error}$ below the 80$^{\rm th}$ percentile
of each cluster's distribution, and by manually excluding stars that
were obvious photometric binaries in the CMD.  We then passed a moving
box average and standard deviation across the CMD in 0.10\,mag bins,
fitted a univariate spline to the binned values, and assembled a
piecewise grid of hybrid isochrones spanning the ages between UCL to
the Pleiades following Equations~6 and~7 from
\citet{gagne_mutau_2020}.

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades,
and a 16\,Myr age for UCL \citep{dahm_2015,pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with slightly older ages being
preferred by the lithium-depletion-boundary (LDB) measurements and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,dobbie_ic_2010,david_ages_2015,randich_gaiaeso_2018,bossini_age_2019,bouma_cluster_2020}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse case of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age as our reference, yielding an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST
isochrone models over a grid of ages, metallicities, and
reddenings, yielded the best agreement for this $\approx 38\,$Myr age
as well, given ${\rm [Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CMD reddening
is higher than the \citet{lallement_threedimensional_2018} value by a factor of two.
} While detailed analyses of the LDB or main-sequence turn-off in the
\cn\ could help resolve the tension between the LDB and isochrone
ages, these are beyond our scope.

@@

We cleaned the candidate TESS rotation period measurements through a
combination of automated and manual steps.  As a matter of scope, we
restricted our attention to the \nkinwithtess\ stars in the spatial
and kinematic proximity of Kepler\,1627, as discussed in
Appendix~\ref{app:kinematicselection}.  We also only focused on stars
for which no companions were known with a brightness exceeding
one-tenth of the target star within a $21\farcs0$ radius: there were
\nkinwithtessandcrowding\ stars that met these requirements, and that
had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the rotation period signal itself:
we required the Lomb Scargle power to exceed 0.2, and the period to be
below 15\,days.

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a
gyrochronological age for the \cn\ below 100\,Myr.  Approximately 10
stars appear as outliers above the ``slow sequence''.  Assuming that
they are all false positives ({\it i.e.}, field interlopers), the
rotation period detection fraction would be
$\nrotgood/\nkinwithtessandcrowding \approx \nfracprot\%$.

Binarity is known to be an important factor in the density of stars
falling underneath the slow sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.
Appendix~\ref{app:rotationbinarity} discusses this topic, and finds
evidence for similar effects to those that have been previously
discussed in the literature.

@@

In brief, the age of the \cn\ cluster based on the empirical
fitting procedure described in Section~\ref{sec:cmd} is
\clusterage.  This procedure hinges on the age adopted for
IC\,2602, since it is the closest reference cluster in the
color-magnitude diagram.  Gyrochronologically, while most of the G and
K dwarfs in the \cn\ have not yet converged to a slow sequence, their
rotation distribution and that of the F dwarfs is consistent with the
same age.  The rotation periods of other 30\,Myr to 50\,Myr clusters
({\it e.g.}, IC\,2602 and IC\,2391) are indistinguishable
\citep{douglas_stephanie_t_2021_5131306}.  The most precise age for \sn\ and its
planet are therefore also \clusterage\ Myr, based on the star's
spatial, kinematic, and rotational connection to this larger ensemble,
and the assumption that the planet formed very quickly after the star.

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet.  The utility
of this element for age dating young stars has been reviewed by
\citet{soderblom_ages_2014}.  We acquired an iodine-free spectrum from
Keck/HIRES on the night of 26 March 2021 using the standard setup and
reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we find ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}\,$m\AA.   Note that this value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Given the stellar
parameters of \sn\ (Table~\ref{tab:starparams}), most notably its
effective temperature, this measurement is also in agreement with an
age for the star between 30\,Myr and 50\,Myr (see {\it e.g.}, Figure~9
of \citealt{bouma_2021_ngc2516}, or the data from
\citealt{randich_gaiaeso_2018}).

@@

		\subfloat{
			\includegraphics[width=0.87\textwidth]{f5.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
    30 minute cadence.  A one hundred day segment is shown here.  The
    {\it top panel} shows the \texttt{PDCSAP} median-subtracted flux
    in units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The model for the stellar
    variability (orange line) is subtracted below, revealing the
    transits of \pn, as well as other deviations from the stellar
    variability model.  The Figure Set available online shows the
    entire 3.9 years of available data.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627b, with stellar variability
    removed.  The 2-$\sigma$ model uncertainties and the maximum {\it
    a posteriori} model are shown as the faint purple band, and the
    dark purple line.  Gray points are individual \texttt{PDCSAP} flux
    measurements; black points are binned to 20 minutes, with a
    representative error bar shown.  The asymmetric residual visible
    during the transit is robust against detrending methods; we
    believe it is caused by starspot crossings.
    \label{fig:lc}
  }
\end{figure*}

@@

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local slope
    of the light curve.  The two quantities appear anti-correlated,
    which is most easily explained by starspot crossings during the
    first (second) half of transit inducing a positive (negative) TTV,
    provided that the orbit is prograde \citep{mazeh_time_2015}.  The
    units along the abscissa are most easily understood by considering
    that the flux from the star changes by $\sim$60\,ppt per half
    rotation period ($\sim$1.3\,days).
    {\it Bottom:} Radial velocities from
    Keck/HIRES during a transit on 7 Aug 2021 UT, observed
    simultaneously with MUSCAT3 ({\it griz} photometry).  A quadratic baseline trend was
    allowed in the RV fit.  The best-fit sky-projected obliquity in this
    model is listed in red; the detection however has marginal
    statistical significance compared to a ``trend-only'' model.
    \label{fig:obliquity}
	}
\end{figure}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Radii, orbital periods, and ages of known transiting
    exoplanets}.  Planets older than
    $10^9$ years are shown with gray markers.  Planets younger than a
    gigayear, with $t/\sigma_t > 3$, are shown in color.  
    \pn\ is shown with a star.
    The abnormally large radii of the youngest transiting planets
    could be explained by their primordial atmospheres not yet
    having evaporated; direct measurements of the atmospheric outflows
    or planetary masses would help to confirm this picture.
    Selection effects may also be important.
    Parameters are from the NASA Exoplanet Archive (July
    2, 2021).
		\label{fig:rp_period_age}
	}
\end{figure*}

>>>>

% 208 words (250 max)
\begin{abstract}
  Kepler\,1627A is a G8V star previously known to host a
  $3.3\,R_\oplus$ mini-Neptune on a 7.2\,day orbit.  The star was
  observed by the Kepler satellite because it is nearby
  ($d=329\pm3\,{\rm pc}$) and it resembles the Sun.  Here we show that
  Kepler\,1627 is a member of the \clusterage\ old $\delta$~Lyr
  cluster using kinematic information from Gaia, stellar rotation
  periods from TESS, and Li abundances from ground-based spectra.  To
  our knowledge, Kepler\,1627Ab is the youngest planet with a precise
  age yet found by the main Kepler mission.  From unresolved
  starspot-crossing events in the Kepler photometry and
  a Keck/HIRES transit we find that the planet is likely on an
  orbit aligned with the stellar spin axis.  We also briefly explore the flare
  arrival time distribution in the short-cadence Kepler
  photometry.
  The $\delta$~Lyr cluster is one of many stellar groups whose
  properties have been clarified using the Gaia data; many other new
  clusters also overlap with confirmed and candidate exoplanets.
  Verifying the results of Gaia clustering analyses using TESS rotation
  periods seems likely to be an effective path toward expanding the census of
  age-dated planets, and our understanding of planetary evolution.
\end{abstract}

@@

%TODO: might want to revise this text to better frame the boil-off phase...
%TODO: better citations on radius evolution?
For instance, the ``mini-Neptunes'', thought to be made of molten
rocky cores \citep{kite_atmosphere_2020} and extended atmospheric
envelopes of hydrogen and helium, are expected to shrink in size by
factors of several over their first $10^8$ years
\citep{owen_atmospheres_2016,owen_constraining_2020}.  Specifically,
they start with sizes of 4--12\,$R_\oplus$ shortly after the time of disk
dispersal ($\lesssim$$10^7$\,years), and shrink to sizes of
2--4\,$R_\oplus$ by 10$^8$ years.  While the majority of this change
is expected to occur within the first few million years of disk
dispersal \citep{owen_atmospheres_2016}, the combination of stellar
irradiation and internal heat may also power a more
gradual outflow which can eventually deplete or entirely strip the
envelope from the rocky core
\citep{Owen_Wu_2013,ginzburg_corepowered_2018}.  Discovering young
planets, measuring their masses, and detecting their atmospheric
outflows are key steps toward testing this paradigm, which is often
invoked to explain the observed radius distribution of mature
exoplanets \citep{Fulton_et_al_2017}.

The K2 and TESS missions have now enabled the detection of about ten
close-in planets younger than 100 million years, all smaller than
Jupiter
\citep{Mann_K2_33b_2016,David_et_al_2017,david_four_2019,newton_tess_2019,bouma_cluster_2020,plavchan_planet_2020,rizzuto_tess_2020}.
The Kepler mission however has not yielded any planets with precise
ages below one gigayear \citep{Meibom_et_al_2013}.  The reason is that
during the main Kepler mission (2009--2013), only four open
clusters were known in the Kepler field: NGC\,6866, NGC\,6811,
NGC\,6819, and NGC\,6791, with ages spanning 0.7\,Gyr to 9\,Gyr
\citep{meibom_kepler_2011}.  Since that time, analyses of the
kinematic, photometric, and astrometric Gaia data have expanded our
knowledge of open cluster and moving group memberships \citep[{\it
e.g.},][]{cantatgaudin_gaia_2018,zari_3d_2018,kounkel_untangling_2019,Meingast2021,kerr_stars_2021}.
As part of our Cluster Difference Imaging Photometric Survey (CDIPS,
\citealt{bouma_cdipsI_2019}), we concatenated the available analyses
from the literature, which yielded a list of candidate young and
age-dated stars (see Appendix~\ref{app:targetlist}).

@@

A previous clustering analysis of the Gaia data reported that
Kepler\,1627 (KIC 6184894; KOI 5245; TIC 120105470) is a member of the
\cn\ \citep{kounkel_untangling_2019}.  Given the previous statistical
validation the close-in mini-Neptune Kepler 1627b
\citep{2012ApJS..199...24T,morton_false_2016,thompson_planetary_2018},
we examined the age of the star and its putative host cluster more
closely (Section~\ref{sec:cluster}).  We find that the $\delta$ Lyr
cluster is \clusterage\ old, and that \sn\ is indeed a member
of the cluster.  Focusing on the planet itself,
we confirm that despite the presence of a previously unreported binary companion,
the planet orbits the G-dwarf primary on an orbit that appears aligned
with the stellar rotation axis
(Section~\ref{sec:planet}).  We conclude by
highlighting broader implications for our ability to age-date a
statistical sample of planets (Section~\ref{sec:conc}).

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.48\textwidth]{f2.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Kepler and TESS views of the $\delta$\,Lyr cluster.} Colored
    points are kinematically selected members of the $\delta$\,Lyr
    cluster.  Both Kepler (gray squares) and TESS observed portions of
    the cluster.  Naked-eye stars ($m_{\rm V}<6.5$) are shown in gray;
    four of them (orange circles) are annotated.
    Kepler\,1627 (green star) was observed during the entirety of the
    Kepler mission, and has been observed by TESS for two lunar months
    to date.  The colors of the other cluster members indicate the
    number of TESS sectors during which they have been observed.
    \label{fig:skychart}
	}
\end{figure}

@@

		\vspace{-0.5cm}
		\subfloat{
			\includegraphics[width=0.8\textwidth]{f15c.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf The \cn\ is \clusterage\ old.}  {\it Top:}
    Color-magnitude diagram of the \cn, IC\,2602 ($\approx38$\,Myr),
    the Pleiades ($\approx 115$\,Myr; \citealt{dahm_2015}), and the
    Gaia EDR3 Catalog of Nearby Stars (gray background;
    log-stretch density).  The right panel provides a zoomed view of stars on
    the pre-main-sequence.  The \cn\ and IC\,2602 are approximately
    the same isochronal age.  {\it Bottom:} TESS and Kepler stellar
    rotation periods versus dereddened Gaia colors, with the Pleiades
    and Praesepe (650\,Myr) shown for reference
    \citep{rebull_rotation_2016a,douglas_poking_2017}.  The \cn\ is
    gyrochronally younger than the Pleiades.
   \label{fig:age}
	}
\end{figure*}

@@

We measured the isochrone age through an empirical approach.  The left
panel of Figure~\ref{fig:age} shows the color-magnitude diagram (CMD)
of stars in the \cn, IC\,2602, the Pleiades, and the field.  The
candidate \cn\ members shown are
selected based on their positions and
kinematics, as discussed in Appendix~\ref{app:kinematicselection}.
Those from the Pleiades and IC\,2602 are adopted from
\citet{cantatgaudin_gaia_2018}, and the field stars are from the Gaia
EDR3 Catalog of Nearby Stars \citep{gaia_gcns_2021}.  We cleaned these
following the data filtering criteria discussed in Appendix~B of
\citet{GaiaCollaboration2018}, except that we weakened the parallax
precision requirement to $\varpi/\sigma_\varpi>5$.  These filters were
designed to include genuine binaries while omitting instrumental
artifacts.  We then corrected for extinction by querying the
3-dimensional maps of \citet{capitanio_threedimensional_2017} and
\citet{lallement_threedimensional_2018}\footnote{\url{https://stilism.obspm.fr/}},
and then applied the extinction coefficients $k_X\equiv A_X/A_0$
computed by \citet{GaiaCollaboration2018} and assumed that $A_0 =
3.1 E(B-V)$.  For IC\,2602, the Pleiades, and the \cn, this procedure
yielded a respective mean and standard deviation for the reddening of
$E(B-V)=\{0.020\pm0.003, 0.045\pm0.008, 0.032\pm0.006\}$.  These
values agree reasonably well with previously reported values from the
literature \citep[{\it
e.g.},][]{GaiaCollaboration2018,kounkel_untangling_2019,bossini_age_2019}.

@@

Figure~\ref{fig:age} shows that the \cn\ and IC\,2602 overlap, and are
therefore approximately the same age.  In our exploration, we also
compared against $\mu$-Tau ($62\pm7$\,Myr; \citealt{gagne_mutau_2020})
and the Upper-Centaurus-Lupus (UCL) component of the Sco OB2
association ($\approx$$16$\,Myr; \citealt{pecaut_star_2016}).  The
pre-main-sequence M dwarfs of the \cn\ were intermediate between these
latter two groups.  To turn this heuristic interpolation into an
age measurement, we used the empirical method
developed by \citet{gagne_mutau_2020}.  In brief, we fitted the
pre-main-sequence loci of a set of reference clusters, and the locus
of the target \cn\ was then modeled as a piecewise linear combination
of these reference clusters.  For our reference clusters, we adopted
members of UCL, IC\,2602, and the Pleiades from
\citet{damiani_stellar_2019} and \cite{CantatGaudin2018a}
respectively.  We removed binaries by requiring $\texttt{RUWE}<1.3$,
$\texttt{radial\_velocity\_error}$ below the 80$^{\rm th}$ percentile
of each cluster's distribution, and manually excluded stars that
were obvious photometric binaries in the CMD.  We then passed a moving
box average and standard deviation across the CMD in 0.10\,mag bins,
fitted a univariate spline to the binned values, and assembled a
piecewise grid of hybrid isochrones spanning the ages between UCL to
the Pleiades following Equations~6 and~7 from
\citet{gagne_mutau_2020}.

@@

The ages returned by this procedure depend on the ages assumed for
each reference cluster.  We adopted a 115\,Myr age for the Pleiades,
and a 16\,Myr age for UCL \citep{dahm_2015,pecaut_star_2016}.  The age
of IC\,2602 however is the most important ingredient, since it
receives the most weight in the interpolation.  Plausible ages for
IC\,2602 span 30\,Myr to 46\,Myr, with slightly older ages being
preferred by the lithium-depletion-boundary (LDB) measurements and
younger ages by the main-sequence turn-off
\citep{stauffer_rotational_1997,dobbie_ic_2010,david_ages_2015,randich_gaiaeso_2018,bossini_age_2019,bouma_cluster_2020}.
If we were to adopt the 30\,Myr age for IC\,2602, then the \cn\ would
be $31^{+5}_{-4}$\,Myr old.  For the converse case of 46\,Myr, the
\cn\ would be $44^{+8}_{-7}$\,Myr old.  We adopt an intermediate
38\,Myr age for IC\,2602, which yields an age for the \cn\ of
\clusterage.\footnote{Our exploration of the PARSEC and MIST
isochrone models over a grid of ages, metallicities, and
reddenings, yielded the best agreement for this $\approx 38\,$Myr age
as well, given ${\rm [Fe/H] = +0.1}$ and $A_V=0.2$
\citep{bressan_parsec_2012,choi_mesa_2016};  this preferred CMD reddening
is higher than the \citet{lallement_threedimensional_2018} value by a factor of two.
} While detailed analyses of the LDB or main-sequence turn-off in the
\cn\ could help resolve the tension between the LDB and isochrone
ages, these are beyond our scope.

@@

We cleaned the candidate TESS rotation period measurements through a
combination of automated and manual steps.  As a matter of scope, we
restricted our attention to the \nkinwithtess\ stars discussed in
Appendix~\ref{app:kinematicselection} in the spatial
and kinematic proximity of Kepler\,1627.  To avoid blending, we also only focused on stars
for which no companions were known with a brightness exceeding
one-tenth of the target star in a $21\farcs0$ radius.  There were
\nkinwithtessandcrowding\ stars that met these requirements, and that
had TESS data available.  For plotting purposes we then imposed a
selection based on the strength of the signal itself:
we required the Lomb Scargle power to exceed 0.2, and the period to be
below 15\,days.

The lower panel of Figure~\ref{fig:age} shows the resulting
\nkindefaultcleaning\ stars.  The majority of these stars fall below
the ``slow sequence'' of the Pleiades, consistent with a
gyrochronological age for the \cn\ below 100\,Myr.  Approximately 10
stars appear as outliers above the ``slow sequence''.  Assuming that
they are all false positives ({\it i.e.}, field interlopers), the
rotation period detection fraction would be
$\nrotgood/\nkinwithtessandcrowding \approx \nfracprot\%$.
The rotation periods of other 30\,Myr to 50\,Myr clusters
({\it e.g.}, IC\,2602 and IC\,2391) are indistinguishable
\citep{douglas_stephanie_t_2021_5131306}.

Binarity is known to be an important factor in the density of stars
falling underneath the slow sequence
\citep{meibom_effect_2007,gillen_ngts_2020,bouma_2021_ngc2516}.
Appendix~\ref{app:rotationbinarity} discusses this topic, and finds
evidence for similar effects to those that have been previously
noted in the literature.

@@

To summarize, the age of the \cn\ cluster based on the empirical
procedure described in Section~\ref{sec:cmd} is
\clusterage.  This procedure hinges on the age adopted for
IC\,2602, since it is the closest reference cluster in the
color-magnitude diagram.  Gyrochronologically, while most of the G and
K dwarfs in the \cn\ have not yet converged to a slow sequence, their
rotation periods and those of the F dwarfs are also consistent with a
30 to 50\,Myr age. The most precise age for \sn\ and its
planet are therefore also \clusterage\ Myr, based on the star's
spatial, kinematic, and rotational connection to the cluster,
and the assumption that the planet formed very quickly after the star.

Beyond the kinematic and rotational lines of evidence for the youth of
\sn, there is a final consistency check: the abundance of
Li\,\textsc{I} as inferred from the 6708\,\AA\ doublet
\citep[see {\it e.g.},]{soderblom_ages_2014}.
We acquired an iodine-free spectrum from
Keck/HIRES on the night of 26 March 2021 using the standard setup and
reduction techniques of the California Planet Survey
\citep{howard_cps_2010}.  Following the equivalent width measurement
procedure described by \citet{bouma_2021_ngc2516}, we find ${\rm
EW}_{\rm Li} = 233^{+5}_{-7}$\,m\AA.   Note that this value does not
correct for the Fe\,\textsc{I} blend at 6707.44\AA.  Given the stellar
parameters of \sn\ (Table~\ref{tab:starparams}), most notably its
effective temperature, this measurement is also in agreement with an
age for the star between 30\,Myr and 50\,Myr ({\it e.g.}, 
\citealt{randich_gaiaeso_2018}; \citealt{bouma_2021_ngc2516}).

@@

		\subfloat{
			\includegraphics[width=0.87\textwidth]{f5.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The light curve of Kepler\,1627.}
    {\it Top}: 
    The full Kepler dataset spans 1{,}437 days (3.9 years), sampled at
    30 minute cadence.  A one hundred day segment is shown here.  The
    {\it top panel} shows the \texttt{PDCSAP} median-subtracted flux
    in units of parts-per-thousand ($\times 10^{-3}$).  The dominant
    signal is induced by starspots.  The model for the stellar
    variability (orange line) is subtracted below, revealing the
    transits of \pn, as well as other deviations from the stellar
    variability model.  The Figure Set available online shows the
    entire 3.9 years of observations.
    {\it Bottom}:
    Phase-folded transit of Kepler 1627b, with stellar variability
    removed.  The 2-$\sigma$ model uncertainties and the maximum {\it
    a posteriori} model are shown as the faint purple band, and the
    dark purple line.  Gray points are individual \texttt{PDCSAP} flux
    measurements; black points are binned to 20 minutes, with a
    representative error bar shown.  The asymmetric residual visible
    during the transit is robust against detrending methods; we
    believe it is caused by starspot crossings.
    \label{fig:lc}
  }
\end{figure*}

@@

		\subfloat{
			\includegraphics[width=0.49\textwidth]{f16.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Evidence for a prograde orbit of Kepler 1627 Ab.}
    {\it Top:} 
    The time of each Kepler transit was measured, along with the local
    slope of the light curve.  The two quantities appear
    anti-correlated, which is most easily explained by starspot
    crossings during the first (second) half of transit inducing a
    positive (negative) TTV, provided that the orbit is prograde
    \citep{mazeh_time_2015}.  The units along the abscissa are most
    easily understood by considering that the flux from the star
    changes by $\sim$60\,ppt per half rotation period
    ($\sim$1.3\,days).
    {\it Bottom:} Radial velocities from Keck/HIRES during a transit
    on 7 Aug 2021 UT, observed simultaneously with MuSCAT3 ({\it griz}
    photometry).  A quadratic baseline trend was allowed in the RV
    fit.  The best-fit sky-projected obliquity in this model is listed
    in red; the detection however has marginal statistical
    significance compared to a ``trend-only'' model.
    \label{fig:obliquity}
	}
\end{figure}

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f14.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Radii, orbital periods, and ages of known transiting
    exoplanets}.  Planets older than $10^9$ years are shown with gray
    markers.  Planets younger than a gigayear, with $t/\sigma_t > 3$,
    are shown in color.  \pn\ is shown with a star.  The large radii
    of the youngest transiting planets could be explained by their
    primordial atmospheres not yet having evaporated; direct
    measurements of the atmospheric outflows or planetary masses would
    help to confirm this expectation.  Selection effects may also be
    important.  Parameters are from the NASA Exoplanet Archive (July
    2, 2021).
		\label{fig:rp_period_age}
	}
\end{figure*}

%, which is expected to be outflowing at a rate of
%$\sim$$10^{-2}$\,$M_\oplus\,{\rm Myr}^{-1}$ \citep[{\it
%e.g.},][]{owen_constraining_2020}.

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  More
precise observations of the Doppler transit could yield a more precise
stellar obliquity, and a means for verifying the expected prograde
orbit.  Similar transit
spectroscopy aimed at detecting either hydrogen or helium absorption
could yield insight into the stability of the planet's atmosphere
\citep[{\it e.g.},][]{spake_helium_2018,vissapragada_2020}.  A more
challenging measurement would be to determine the planet's mass,
either through detailed timing analyses of the Kepler data, or through
a high-cadence multi-color radial velocity campaign.  The mass,
measured at sufficient precision, could yield constraints on both the
planet's composition as well as its initial entropy
\citep{owen_constraining_2020}.
